The Feasibility of Stylometry as a Service

### 2013-12-04 paper/paper.tex
Enhanced Introduction

\section*{Motivation}\label{sec:motivation}

@@

Migrating to a web service would provide JSAN with several benefits.
This web service would provide adversarial stylometry capabilities to
embedded devices like tablets or smart-phones which otherwise could
not run the software natively.  Since there would be no installation,
besides a typical web-browser, a web-service would be better suited
for time-critical situations where an author must quickly anonymize
her document.  Lastly, we believe that a stylometric service could
increase anonymity.

An effective technique in adversarial stylometry is imitation of
another author's writing style.  However, since many are not trained
author imitators, this technique requires significant cognitive effort.
Perhaps a more effective technique, would be to have multiple authors
re-write the target work in their natural style.  This would be
difficult to accomplish with standalone software, but with a web
service with multiple users, this is feasible.

>>>>

\section*{Introduction}\label{sec:intro}

@@

Migrating to a web service would provide JSAN with several benefits.
This web service would provide adversarial stylometry capabilities to
embedded devices like tablets or smart-phones which otherwise could
not run the software natively.  Since there would be no installation,
besides a typical web-browser, a web-service would be better suited
for time-critical situations where an author must quickly anonymize
her document.

An example use-case is an author with a time sensitive document that
she needs to release.  Because of the sensitive nature, she wishes to
apply adversarial stylometry to her document.  In this case, a
computer with decent enough performance to natively run machine
learning techniques may not be available.  However, a web service is
nearly ubiquitous.

\subsection{Expanding Stylometric Research}

A stylometric web service also expands research opportunities.  This
service, offered through a modern architecture, would allow
researchers to easily perform experiments.  An easily accessible tool
allows for rapid verification of research results and greater
community engagement.

In addition to convenient access, a web service can provide additional
diversity in stylometric experimentation.  For example, this web
service supports multiple authors and provides a better tool for
real-time, multiple author stylometry than a stand-alone application.

An effective technique in adversarial stylometry is imitation of
another author's writing style.  However, since many are not trained
author imitators, this technique requires significant cognitive effort.
Perhaps a more effective technique, would be to have multiple authors
re-write the target work in their natural style.  While there has been
numerous studies into single author stylometric analysis, multiple
authorship is more difficult.  This web services provides a platform
for multiple authorship research.

\subsection{Challenges in a Web Service}

A privacy enhancing technology that is designed to exist as a web
service faces different challenges than an application.  Attack
vectors open up on the service from active denial-of-service attacks
to passive sniffing.  A privacy web service must take great care to
ensure that service does not compromise its user's privacy.  In
Section \ref{sec:design} we provide our architecture and analysis the
security and privacy.
